Chapter 3: Appendix

### 2021-03-30 appendix_chapter_3.Rmd
appendix corrections

When comparing distances between passive and kelp particles for April, significant differences are evident. (Figure 11, simulations 17-29; p < 0.05). Kelp particles with only 90% hydrodynamic and 10% wind drag across cross-sectional areas travelled shorter distance across compared to other kelp particles. The shortest distance travelled was the scenario with the maximum cross-sectional area and drag exposure scenarios. No significant differences are evident for the July simulations, with only slight variation across simulations (see Figure 11, simulations 30-42; p > 0.05). In October, the plot shows significant differences when comparing both passive and kelp particles (see Figure 11, simulations 43-55; p < 0.05). Kelp particles with only 90% hydrodynamic drag across cross-sectional areas travelled shorter distance compared to all other particles. As seen in the April simulations, the kelp particles with the maximum cross-sectional area and drag exposure travelled the shortest distance compared to all other particles.

>>>>

When comparing distances between passive and kelp particles for April, significant differences are evident. (Figure 11, simulations 17-29; *p* < 0.05). Kelp particles with only 90% hydrodynamic and 10% wind drag across cross-sectional areas travelled shorter distance across compared to other kelp particles. The shortest distance travelled was the scenario with the maximum cross-sectional area and drag exposure scenarios. No significant differences are evident for the July simulations, with only slight variation across simulations (see Figure 11, simulations 30-42; *p* > 0.05). In October, the plot shows significant differences when comparing both passive and kelp particles (see Figure 11, simulations 43-55; *p* < 0.05). Kelp particles with only 90% hydrodynamic drag across cross-sectional areas travelled shorter distance compared to all other particles. As seen in the April simulations, the kelp particles with the maximum cross-sectional area and drag exposure travelled the shortest distance compared to all other particles.
